Something with Objects and Names

### 2019-12-04 papers/ACL2020/experiments.tex
[ACL2020] fixes hyper-hypo bug in experiments.tex
[ACL2020] experiments.tex

	\midrule
	FRCNN--VG1600 & VG     &                 0.06 
		&            0.02 &                 0.0 &                  0.16 &           0.06 &           0.49 &             0.20 &                 0.03 &            0.05 &                 0.0 &                  0.16 &           0.13 &           0.50 &             0.13 \\
	FRCNN--MN442 & VG       &                 0.06 
		&            0.01 &                 0.0 &                  0.15 &           0.06 &           0.60 &             0.13 &                 0.02 &            0.02 &                 0.0 &                  0.13 &           0.11 &           0.60 &             0.11 \\
	\midrule \midrule
	FRCNN--VG1600--VGMN & MN &                 0.14 
		&            0.01 &                 0.0 &                  0.12 &           0.05 &           0.50 &             0.17 &                 0.11 &            0.03 &                 0.0 &                  0.16 &           0.11 &           0.50 &             0.11 \\
	\midrule
		ResNet101--VGMN & MN		&                 0.11 &             0.0 &                 0.0 &                  0.12 &           0.01 &           0.64 &             0.11 &                 0.03 &             0.0 &                 0.0 &                  0.12 &           0.05 &           0.69 &             0.10 \\
	ResNet101--MN442 & MN &                 0.09 
		&             0.0 &                 0.0 &                  0.13 &           0.02 &           0.63 &             0.13 &                 0.05 &             0.0 &                 0.0 &                  0.15 &           0.07 &           0.62 &             0.12 \\
	ResNet101--VGMN & VG &                 0.10 
			&             0.0 &                 0.0 &                  0.06 &           0.02 
			&           0.69 &             0.12 
		&  0.04 
			&             0.0 &                 0.0 &                  0.03 &           0.06 
			&           0.67 &             0.20 \\ 
	ResNet101--MN442 & VG &                 0.08 &             0.0 &                 0.0 &                  0.07 &           0.03 &           0.69 &             0.13 &                 0.01 &             0.0 &                 0.0 &                  0.06 &           0.08 &           0.62 &             0.23 \\
	\bottomrule
\end{tabular}
\caption{Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
\end{table*}

>>>>

	\midrule
	FRCNN--VG1600 & VG     &                 6 
		&            2 & 0 &                   16 &           6 &           49 &             20 &                 3 &            5 & 0 &                   16 &           13 &           50 &             13 \\
	FRCNN--MN442 & VG       &                 6 
		&            1 & 0 &                   15 &           6 &           60 &             13 &                 2 &            2 & 0 &                   13 &           11 &           60 &             11 \\
	\midrule \midrule
	FRCNN--VG1600--VGMN & MN &                 14 
		&            1 & 0 &                   12 &           5 &           50 &             17 &                 11 &            3 & 0 &                   16 &           11 &           50 &             11 \\
	\midrule
		ResNet101--VGMN & MN		&                 11 & 0 &  0 &                   12 &           1 &           64 &             11 &                 3 & 0 &  0 &                   12 &           5 &           69 &             10 \\
	ResNet101--MN442 & MN &                 9 
		& 0 &  0 &                   13 &           2 &           63 &             13 &                 5 & 0 &  0 &                   15 &           7 &           62 &             12 \\
	ResNet101--VGMN & VG &                 10 
			& 0 &  0 &                   6 &           2 
			&           69 &             12 
		&  4 
			& 0 &  0 &                   3 &           6 
			&           67 &             20 \\ 
	ResNet101--MN442 & VG &                 8 & 0 &  0 &                   7 &           3 &           69 &             13 &                 1 & 0 &  0 &                   6 &           8 &           62 &             23 \\
	\bottomrule
\end{tabular}
\caption{Results in \%. Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
\end{table*}
